### 2015-05-23 docs/report/array_sharing.tex
Corrections up to code sharing

As explained in section~\ref{sec:serialization-and-transference} of this document transferring \ttarray{} objects to and from workers requires the use of \code{Transferable}s to achieve acceptable performance. Since our library will receive \ttarray{} objects to be partiotioned and handled between multiple workers, it is important that it takes as little time as possible for the partitioning of the arrays.

If the library is configured to use \(N\) workers then the original data in the \ttarray{} will copied into \(N\) smaller \ttarray{}s. For ideal performance it would be nice to be able to pass a pointer into the array and an amount of elements to process, but since there's no shared memory and element ownership is tranferred to the Web Workers the elements must be copied to the sub-arrays.

@@

\subsubsection{Conclusion}
The benchmark shows that there are three very similar alternatives to split a \ttarray{}. We are going to use \textit{Buffer subarray} as it yields better performance in a newer version of Chrome. The implementation of the slice function could look something like this:
\begin{lstlisting}[caption=Function to benchmark]
function typedArraySlice(array, from, to) {
  return new array.constructor(array.subarray(from, to));
}
\end{lstlisting}

>>>>

As explained in section~\ref{sec:serialization-and-transference} of this document, transferring \ttarray{} objects to and from workers requires the use of \code{Transferable}s to achieve acceptable performance. Since our library will receive \ttarray{} objects to be partitioned and handed over to multiple workers, it is important that it takes as little time as possible for the partitioning of the arrays.\footnote{This does not apply to \tstarray{}s as those can be transferred without being partitioned}

If the library is configured to use \(N\) workers then the original data in the \ttarray{} will copied into \(N\) smaller \ttarray{}s. For ideal performance it would be nice to be able to pass a pointer into the array and an amount of elements to process, but \ttarray{}s do not support shared memory and element ownership is tranferred to the Web Workers, the elements must be copied to the sub-arrays.

@@

\subsubsection{Conclusion}
The benchmark shows that there are three very similar alternatives to partition a \ttarray{}. We are going to use \textit{Buffer subarray} as it yields better performance in a newer version of Chrome. The implementation of the slice function could look something like this:
\begin{lstlisting}[caption=Possible approach to copy a slice of a \ttarray{}]
function typedArraySlice(array, from, to) {
  return new array.constructor(array.subarray(from, to));
}
\end{lstlisting}

### 2015-05-23 docs/report/serialization_transference.tex
Corrections up to code sharing

Let's assume that we have an array of \code{N} elements on which we want to perform a particular transformation through the \code{map} function. If we run in a single thread (no parallelism) and the average time to process is element is \code{t} then we could approximate the total time \(T_{ser}\) for the operation as:
\[T_{ser} = \sum_{i = 0}^{N}t = Nt\]

@@

Based on the previous equations we deduce that we can reduce \(T_{sync}\) the closer to the best possible scenario we will be.

In our case we are trying to transfer objects between a browser's JavaScript UI thread and Web Workers so we are constrained by the means of that environment. The Worker interface is the following \cite{w3c-ww}:
\begin{lstlisting}[language=Java, caption=The Worker interface]
[Constructor(DOMString scriptURL)]
interface Worker : EventTarget {
  void terminate();

@@

As the aforementioned interface states one can either send just a message or send a message with a sequence of transferable objects. From section \textbf{2.7.5} of the HTML Standard \cite{html-whatwg}:
\textit{``Some objects support being copied and closed in one operation. This is called transferring the object, and is used in particular to transfer ownership of unsharable or expensive resources across worker boundaries."}

Considering the definition of a \code{Transferable} the latter seems like a good alternative to minimize both \(T_{s}\) and \(T_{s}\). Even more so when one considers that otherwise objects are copied using structured cloning(explained in section \textbf{2.7.6} of that same standard).

\subsection{Benchmarks}
To verify the above we put together two benchmarks that aim to verify the difference between invoking \code{postMessage} with and without structured cloning for a \ttarray{}. Both transfer a \ttarray{} back and forth between the UI thread and a worker; the only difference between the two is that one has 100000 (a hundred thousand) elements in the \ttarray{} and the other one 1000000 (a million).

\subsubsection{With 100000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/transferrable-vs-cloning}{../../spikes/1.2/transferrableVsCloning.js}

The results for it are displayed in Figure~\ref{fig:transferrable-vs-cloning}.
\img{Results with 100000 elements}{../../spikes/1.2/transferrableVsCloning}{fig:transferrable-vs-cloning}

\subsubsection{With 1000000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/longer-transferrable-vs-cloning}{../../spikes/1.2/longerTransferrableVsCloning.js}

The results for it are displayed in Figure~\ref{fig:long-transferrable-vs-cloning}.
\img{Results with 100000 elements}{../../spikes/1.2/longerTransferrableVsCloning}{fig:long-transferrable-vs-cloning}

\subsubsection{Conclusion}
As we can see from the previous results increasing the amount of elements by 10x does not change the amount of operations that can be performed when using \code{Transferable} objects, it scales. On the other hand, the amount of operations that can be performed with structured cloning greatly decreases.

>>>>

Let's assume that we have an array of \code{N} elements on which we want to perform a particular transformation through the \code{map} function. If code is executed in a single thread (no parallelism) and the average time to process an element is \(t\) then we could approximate the total time \(T_{ser}\) for the operation as:
\[T_{ser} = \sum_{i = 0}^{N}t = Nt\]

@@

Based on the previous equations we deduce that: the more we can reduce \(T_{sync}\), the closer to the best possible scenario we will be.

In our case we are trying to transfer objects between a browser's JavaScript UI thread and Web Workers so we are constrained by the means of that environment. The Worker interface is the following one \cite{w3c-ww}:
\begin{lstlisting}[language=Java, caption=The Worker interface]
[Constructor(DOMString scriptURL)]
interface Worker : EventTarget {
  void terminate();

@@

As the aforementioned interface states, one can either send just a message or send a message with a sequence of transferable objects. From section \textbf{2.7.5} of the HTML Standard \cite{html-whatwg}:
\textit{``Some objects support being copied and closed in one operation. This is called transferring the object, and is used in particular to transfer ownership of unsharable\footnote{Note that the definition does not consider \tsabuffer{} instances as those are sharable and transferable.} or expensive resources across worker boundaries."}

Considering the definition of a \code{Transferable} the latter seems like a good alternative to minimize both \(T_{s}\) and \(T_{s}\). Even more so when one considers that otherwise objects are copied using structured cloning (explained in section \textbf{2.7.6} of that same standard).

\subsection{Benchmarks}
To verify the above we put together two benchmarks that aim to verify the difference between invoking \code{postMessage} with and without structured cloning for a \ttarray{}. Both transfer a \ttarray{} back and forth between the UI thread and a worker; the only difference between the two is that one has 100,000 (a hundred thousand) elements in the \ttarray{} and the other one 1,000,000 (a million).

\subsubsection{With 100,000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/transferrable-vs-cloning}{../../spikes/1.2/transferrableVsCloning.js}

The results for it are displayed in Figure~\ref{fig:transferrable-vs-cloning}.
\img{Results with 100,000 elements}{../../spikes/1.2/transferrableVsCloning}{fig:transferrable-vs-cloning}

\subsubsection{With 1,000,000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/longer-transferrable-vs-cloning}{../../spikes/1.2/longerTransferrableVsCloning.js}

The results for it are displayed in Figure~\ref{fig:long-transferrable-vs-cloning}.
\img{Results with 100,000 elements}{../../spikes/1.2/longerTransferrableVsCloning}{fig:long-transferrable-vs-cloning}

\subsubsection{Conclusion}
As we can see from the previous results, increasing the amount of elements by 10x does not change the amount of operations that can be performed when using \code{Transferable} objects; it scales. On the other hand, the amount of operations that can be performed with structured cloning greatly decreases.
